Topological Equivariant Artist Model

### 2022-01-12 slides/main.tex
flipped arrows, corrected sheaves and presheaves formulas

\begin{frame}{General purpose libraries generally can't\cite{toryRethinkingVisualizationHighlevel2004}}
    \begin{figure}
        \includegraphics[height=.3\textheight]{../paper/figures/k_different_types.png}
    \end{figure}
    \begin{enumerate}
        \item Matplotlib\cite{hunterMatplotlib2DGraphics2007} $\rightarrow$Seaborn\cite{waskom2020seaborn}, xarray \cite{hoyer2017xarray} 
        \item D3 \cite{bostockDataDrivenDocuments2011}
        \item VTK \cite{hanwellVisualizationToolkitVTK2015,geveciVTK2012}(MayaVi\cite{RamachandranMayaVI2011})$\rightarrow$ Titan\cite{brianwylieUnifiedToolkitInformation2009}, ParaView\cite{ahrens2005paraview}
    \end{enumerate}
\end{frame}

\subsection{Algebraic Topology & Category Theory}

\begin{frame}{Mathematical Data Abstraction}
    \begin{description}
        \item[Fiber Bundles] "unified, dimension-independent framework" that expresses data as the mapping between continuity and fields \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}
        %% change SD to Category Theory Langauge - Express structure and constraints [software papers]
        \item[Simplicial Databases] systemic way to apply a schema to a fiber, i.e. provides a way to name fields and bind them to types system (e.g. \texttt{int}, \texttt{float}) 
         \cite{spivakSIMPLICIALDATABASES, spivakDatabasesAreCategories2010} 
        \item[Sheaves on Bundles] "algebraic data structure" for representing data over topological spaces \cite{ghristElementaryAppliedTopology2014}
    \end{description}
\end{frame}

@@

            \item[\textcolor{base}{Continuity Type \dbasec}]{how data elements are organized (topological properties) \cite{wilkinsonGrammarGraphics2005})}

@@

%drop category K and \gamma op slides
\begin{frame}{Category $\mathcal{\dbasec}$}
\begin{columns}
    \column{0.49\textwidth}
\begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \textcolor{source}{C_1} \arrow[r, "f", color=source] \arrow[rd, "g\circ f"', color=source] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source] \& \textcolor{source}{C_2} \arrow[d, "g", color=source] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source] \\
    \& \textcolor{source}{C_3} \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]              
    \end{tikzcd}
    \end{equation*}
    \column{0.49\textwidth}
    \onslide<2-|handout:1>{
    \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
    }
    \end{columns}
\end{frame}

@@

\begin{frame}{$\mathcal{C}^{op}$}
    \begin{columns}
        \column{0.29\textwidth}
        \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
        \column{0.69\textwidth}
        \onslide<2-|handout:1>{
            \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc_1}{\dtotalc\restriction_{\opensetc_1}} \&  \& \cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}} \arrow[ll, "\iota^*\restriction_{\opensetc_1}"', color=set]\\
            \&\&\\\&  \& \cgamma{\opensetc_3}{\dtotalc\restriction_{\opensetc_3}} \arrow[uu, "\iota^*\restriction_{\opensetc_2}"', color=set] \arrow[lluu, "\iota^*\restriction_{\opensetc_2} \circ \textcolor{set}{\iota^*\restriction}_{\opensetc_1}", color=set]
            \end{tikzcd}
        }

        \end{columns}
\end{frame}

@@

%pull back in keys, values 
\begin{frame}{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<9-|handout:1->{\dfiberc}
        \onslide*<9-|handout:1->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:1->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3,6-|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} 
            \onslide*<4-5|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}\in \setc}
            \onslide*<0|handout:1>{\setc \ni {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}}
            \&  
            {} \& 
            \onslide*<6-|handout:1>{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<7-|handout:1>{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<3|handout:0>{\opensetc_1 \subset \dbasec}
            \onslide*<4-5|handout:0>{\opensetc_1 \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}})}
            \onslide*<6-|handout:0>{\opensetc_1}
            \onslide*<0|handout:1>{Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \ni \opensetc_1} 
            \onslide*<5-|handout:0>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<0|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf, shift right = 10]}
            \onslide*<7-|handout:1>{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<8-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}" description, maps to, color=sheaf]} \& 
            \onslide*<6-|handout:1>{\opensetc_2} 
            \onslide*<6-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}"', maps to, color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{center}
        \begin{alertblock}<8-|handout:1>{stalk}
            % F_k is subset of O_{K,E} is 
            % O_{K,E} is the Jet
            \begin{aligned*}
                \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \ \dfiberc_{\dbasepointc}
            \end{aligned*}
        \end{alertblock}

@@

\begin{frame}{Sheaves} %why we care, either drop out or define what an open covering is
    %%% footnote on open covering
    A sheaf is a presheaf that satisfies the following two axioms\cite{bakerMathsSheaf}\\
    \begin{block}<2-|handout:1>{locality}
        if $\mathcal{\opensetc} = \{\opensetc_i\}_{i\in I}$ is an open covering of \opensetc
        \onslide<3-|handout:1>{
        and if $\dsectionc^{a}, \dsectionc^{b} \in \sheafc(\opensetc_i)$ have the property $\dsectionc^{a}\restriction_{\opensetc_i} = \dsectionc^{b}\restriction_{\opensetc_i}$ for each $\opensetc_i \in \mathcal{\opensetc}$,}
        \onslide<4|handout:1>{ then $\dsectionc^{a} = \dsectionc^{b}$}
    \end{block} 
    \begin{block}<5-|handout:1>{gluing} %gluing w/o open covering rule
        if $\mathcal{\opensetc} = \{\opensetc_i\}_{i\in I}$ is an open covering of \opensetc\ and if $\dsectionc^{i} \in \sheafc(\opensetc_i)$ is given for each $i \in I$
        \onslide<6-|handout:1>{such that ${\dsectionc^{i}}\restriction_{\opensetc_i\cap \opensetc_j} = {\dsectionc^{j}}\restriction_{\opensetc_i \cap \opensetc_j}$ for each pair $\opensetc_i, \opensetc_j \in \mathcal{\opensetc}$,}
        \onslide<7-|handout:1>{ then there exists $\dsectionc \in \sheafc(\opensetc)$ such that $\dsectionc\restriction_{\opensetc_i} = {\dsectionc^{i}}$ for each $i \in I$} 
    \end{block}      
\end{frame}

%flip the ordering: K, then G, then functor 

@@

    \frametitle<0|handout:1>{Functor: \vindexc: \mathcal{\gbasec} \rightarrow \mathcal{\dbasec}}
    \frametitle<0|handout:2>{Data}
    \frametitle<0|handout:3>{Pullback: data to region of the visualization} 
    \frametitle<0|handout:4>{Graphic}
    \frametitle<0|handout:5>{Pushforward: visualization to index of data}

@@

            \onslide*<7-8|handout:4-5>{\sheafc_{\gbasec, \gtotalc}} 
            \onslide*<7-8,10-|handout:5>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]} \& \& 
            \onslide*<7-8|handout:5>{\textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc}}  

@@

            \onslide*<2-|handout:1,3->{\gbasec}
            \onslide*<3-|handout:1,3,5>{\arrow[rr, "\vindex", color=functor]}
            \onslide*<7-8,10-|handout:4-5>{\arrow[u, "\sheaf_{\gbasec, \gtotalc}", maps to, color=sheaf]}
            \onslide*<6,8-9,11-|handout:3>{\arrow[d, dashed, maps to, color=sheaf]} \&  \& 
            \onslide*<1-|handout:1-3,5>{\dbasec}
            \onslide*<4-6,8-9,11-|handout:2-3>{\arrow[d, "\sheaf_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<7-8,10-|handout:5>{\arrow[u, dashed, maps to, color=sheaf]} \\
            \onslide*<5-6,8|handout:3>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}} 
            \onslide*<5-6,8-9,11-|handout:3>{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}  \& \& 
            \onslide*<4-6,8|handout:2-3>{\sheafc_{\dbasec, \dtotalc}}

@@

    \only<4|handout:2>{

@@

    \only<6|handout:3>{

@@

    \only<7|handout:4>{

@@

    \only<7|handout:5>{

@@

\end{frame}
.

@@

% pull up artist^*, artist_*
\begin{frame}{
    \only<1-3|handout:1-3>{Natural Transforms Between Sheaves}
    \only<4|handout:4>{$\vartistc:\sheafc_{(\dbasec, \dtotalc)}\rightarrow \sheafc_{(\gbasec, \gtotalc)}$}
    \only<5-|handout:5->{$\vartistc: \dsectionc \mapsto \gsectionc$}
    }
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<1-4|handout:1>{\sheafc_{\gbasec, \gtotalc}\gbasec} 
          \onslide*<1-3|handout:1>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \onslide*<4-|handout:2->{\arrow[rr, "\vindexpushc", color=artist]} 
          \& \& 
          \onslide*<1-4|handout:1>{(\textcolor{functor}{\vindexpush}\sheafc_{(\gbasec, \gtotalc)})(\dbase)}
          \\
          \& \& \\
          \onslide*<1-4|handout:1>{(\textcolor{functor}{\vindexpull}\sheafc_{(\dbasec, \dtotalc)})(\gbasec)}
          \onslide*<1-3|handout:1>{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}
          \onslide*<4-|handout:2->{\arrow[rr, "\vindexpullc", color=artist]}
          \onslide*<2-3|handout:1>{\arrow[uu, "\textcolor{nattran}{Nat_{\gbasec}}", color=nattran]} 
          \onslide*<4-|handout:2->{\arrow[uu, "\vartistc_{\vindexpushc}", color=artist]}
          \&  \& 
          \onslide*<1-4|handout:1->{\sheafc_{\dbasec, \dtotalc}} 
          \onslide*<2-3|handout:1>{\arrow[uu, "\textcolor{nattran}{Nat_{\dbasec}}"', color=nattran]}
          \onslide*<4-|handout:2->{\arrow[uu, "\vartistc_{\vindexpullc}"', color=artist]}
          \onslide*<3|handout:1>{\arrow[lluu, " "' description, dashed, color=nattran]}
          \onslide*<4-|handout:2->{\arrow[lluu, "\vartistc"' description, dashed, color=artist]}
        \end{tikzcd}
      \end{equation*}

@@

\begin{frame}{$\vartist_{\vindexpullc}: \vindexpullc\sheafc_{(\dbasec, \dtotalc)} \rightarrow \sheafc_{(\gbasec, \gtotalc)}$}
    \begin{equation}
  \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\dtotalpullc}", color=sheaf] 
    \arrow[rr, "\sheafc_{\gtotalc}"', color=sheaf] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist] &&&& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\dtotalpullc}"', color=sheaf] 
    \arrow[rr, "\sheafc_{\gtotalc}", color=sheaf] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc}                                                        
\end{tikzcd}
\end{equation}
\end{frame}
\end{comment}

@@

\begin{frame}{Continuty Equivariance $\vindexpullc\hat\dfuncc = \dfuncc|_{\vindexprec}$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement =\&]
            S 
            \arrow[r, "\xi"] 
            \arrow[d, "\xi^*\hat\varphi"'] 
            \& 
            K 
            \arrow[d, "\hat\varphi"] \\
            S^{\prime} 
            \arrow[r, "\xi"]
            \& 
            K^{\prime}
            \end{tikzcd}
    \end{equation*}
\end{frame}
\begin{frame}{Field Equivariance $\tilde\dfuncc \cong \tilde\dfuncc_\gtotalc$}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        {\Gamma(U, E)} 
        \arrow[r, "A"] 
        \arrow[d, "\tilde\varphi\circ\hat\varphi_*"'] 
        \& 
        {\Gamma(W, H)} 
        \arrow[d, "\tilde\varphi_H\circ\xi_*\hat{\varphi}_*"] \\
        {\Gamma(\hat\varphi U, \tilde\varphi\hat\varphi_*E)} 
        \arrow[r, "A"] 
        \& 
        {\Gamma(\xi^*\hat\varphi W, \tilde\varphi_H\xi^*\hat\varphi_*H)}    
    \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{frame}{Equivariant Artist}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        {\mathcal{O}_{K, E}} 
        \arrow[r, "A"] 
        \arrow[d, "\varphi"'] \& 
        {\mathcal{O}_{S,H}} 
        \arrow[d, "\varphi_H"] \\
        {\mathcal{O}_{K^{\prime}, E^{\prime}}} 
        \arrow[r, "A"]    \& 
        {\mathcal{O}_{S^{\prime}, H^{\prime}}}    
        \end{tikzcd} 
    \end{equation*}
        \begin{block}
            \vartistc\ is equivariant when there exists a $\dfuncc_H$ s.t the diagram commutes. 
            \begin{equation*}
            \end{equation*}
        \end{block}
    \end{frame}

>>>>

\begin{frame}{General purpose libraries generally can't\cite{toryRethinkingVisualizationHighlevel2004}}
    \begin{figure}
        \includegraphics[height=.3\textheight]{../paper/figures/k_different_types.png}
    \end{figure}
    \begin{enumerate}
        \item Matplotlib\cite{hunterMatplotlib2DGraphics2007} $\rightarrow$Seaborn\cite{waskom2020seaborn}, xarray \cite{hoyer2017xarray} 
        \item D3 \cite{bostockDataDrivenDocuments2011}
        \item VTK \cite{hanwellVisualizationToolkitVTK2015,geveciVTK2012}(MayaVi\cite{RamachandranMayaVI2011})$\rightarrow$ Titan\cite{brianwylieUnifiedToolkitInformation2009}, ParaView\cite{ahrens2005paraview}
    \end{enumerate}
\end{frame}
\end{comment}

\section{Algebraic Topology & Category Theory}

\begin{frame}{Mathematical Data Abstraction}
    \begin{description}
        \item[Fiber Bundles] "unified, dimension-independent framework" that expresses data as the mapping between continuity and fields \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}
        \item[Category Theory Language] express constraints in specifications \cite{wielsManagementEvolvingSpecifications1998}   
        \item[Sheaves on Bundles] "algebraic data structure" for representing data over topological spaces \cite{ghristElementaryAppliedTopology2014}
    \end{description}
\end{frame}

@@

            \item[\textcolor{base}{Continuity Type \dbasec}]{how data elements are organized (topological properties) \cite{wilkinsonGrammarGraphics2005,munznerWhatDataAbstraction2014})}

@@

@@

@@

\begin{frame}{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<9-|handout:1->{\dfiberc}
        \onslide*<9-|handout:1->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:1->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3,6-|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} 
            \onslide*<4-5|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}\in \setc}
            \onslide*<0|handout:1>{\setc \ni {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}}
            \&  
            {} \& 
            \onslide*<6-|handout:1>{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<7-|handout:1>{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<3|handout:0>{\opensetc_1 \subset \dbasec}
            \onslide*<4-5|handout:0>{\opensetc_1 \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}})}
            \onslide*<6-|handout:0>{\opensetc_1}
            \onslide*<0|handout:1>{Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \ni \opensetc_1} 
            \onslide*<5-|handout:0>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<0|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf, shift right = 10]}
            \onslide*<7-|handout:1>{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<8-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}" description, maps to, color=sheaf]} \& 
            \onslide*<6-|handout:1>{\opensetc_2} 
            \onslide*<6-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}"', maps to, color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{center}
        \begin{alertblock}<8-|handout:1>{stalk}
            \begin{aligned*}
                \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \\
                 \dfiberc_{\dbasepointc} \subset  \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}
            \end{aligned*}
        \end{alertblock}

@@

\begin{frame}{Sheaves} 
    A sheaf is a presheaf that satisfies the following two axioms\cite{bakerMathsSheaf}\\
    \begin{block}<2-|handout:1>{locality}
        if there exists the open covering $\mathcal{\opensetc} = \{\opensetc_i\}_{i\in I}$ of \opensetc
        \onslide<3-|handout:1>{
        and if $\dsectionc^{a}, \dsectionc^{b} \in \sheafc(\opensetc_i)$ have the property $\dsectionc^{a}\restriction_{\opensetc_i} = \dsectionc^{b}\restriction_{\opensetc_i}$ for each $\opensetc_i \in \mathcal{\opensetc}$,}
        \onslide<4|handout:1>{ then $\dsectionc^{a} = \dsectionc^{b}$}
    \end{block} 
    \begin{block}<5-|handout:1>{gluing} 
        if there exists the open covering $\mathcal{\opensetc} = \{\opensetc_i\}_{i\in I}$ of \opensetc\ and if $\dsectionc^{i} \in \sheafc(\opensetc_i)$ is given for each $i \in I$
        \onslide<6-|handout:1>{such that ${\dsectionc^{i}}\restriction_{\opensetc_i\cap \opensetc_j} = {\dsectionc^{j}}\restriction_{\opensetc_i \cap \opensetc_j}$ for each pair $\opensetc_i, \opensetc_j \in \mathcal{\opensetc}$,}
        \onslide<7-|handout:1>{ then there exists $\dsectionc \in \sheafc(\opensetc)$ such that $\dsectionc\restriction_{\opensetc_i} = {\dsectionc^{i}}$ for each $i \in I$} 
    \end{block}      
\end{frame}

@@

    \frametitle<3|handout:3>{Functor: \vindexc: \mathcal{\gbasec} \rightarrow \mathcal{\dbasec}}
    \frametitle<1|handout:1>{Data}
    \frametitle<4-6|handout:4>{Pullback: data to region of the visualization} 
    \frametitle<2|handout:2>{Graphic}
    \frametitle<7-|handout:5>{Pushforward: visualization to index of data}

@@

            \onslide*<0|handout:2,3,5>{\sheafc_{\gbasec, \gtotalc}} 
            \onslide*<0|handout:5>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]} \& \& 
            \onslide*<0|handout:5>{\textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc}}  

@@

            \onslide*<0|handout:2->{\gbasec}
            \onslide*<0|handout:3->{\arrow[rr, "\vindex", color=functor]}
            \onslide*<0|handout:2,3,5>{\arrow[u, "\sheaf_{\gbasec, \gtotalc}", maps to, color=sheaf]}
            \onslide*<0|handout:4>{\arrow[d, dashed, maps to, color=sheaf]} \&  \& 
            \onslide*<0|handout:1,3->{\dbasec}
            \onslide*<0|handout:1,3-4>{\arrow[d, "\sheaf_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<0|handout:5>{\arrow[u, dashed, maps to, color=sheaf]} \\
            \onslide*<0|handout:4>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}} 
             \& \& 
            \onslide*<0|handout:1,3-4>{\sheafc_{\dbasec, \dtotalc}}
            \onslide*<0|handout:4>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 

@@

    \only<0|handout:1>{

@@

    \only<0|handout:4>{

@@

    \only<0|handout:2>{

@@

    \only<0|handout:5>{

@@

@@

\begin{frame}{$\vartist_{\vindexpullc}: \vindexpullc\sheafc_{(\dbasec, \dtotalc)} \rightarrow \sheafc_{(\gbasec, \gtotalc)}$}
    \begin{equation}
  \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\dtotalpullc}", color=sheaf] 
    \arrow[rr, "\sheafc_{\gtotalc}"', color=sheaf] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist] &&&& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\dtotalpullc}"', color=sheaf] 
    \arrow[rr, "\sheafc_{\gtotalc}", color=sheaf] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc}                                                        
\end{tikzcd}
\end{equation}
\end{frame}

\begin{frame}{
    \only<1-3|handout:1-3>{Natural Transforms Between Sheaves}
    \only<4|handout:4>{$\vartistc:\sheafc_{(\dbasec, \dtotalc)}\rightarrow \sheafc_{(\gbasec, \gtotalc)}$}
    \only<5-|handout:5->{$\vartistc: \dsectionc \mapsto \gsectionc$}
    }
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<1-4|handout:1>{\sheafc_{\gbasec, \gtotalc}\gbasec} 
          \onslide*<1-3|handout:1>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \onslide*<4-|handout:2->{\arrow[rr, "\vindexpushc", color=artist]} 
          \& \& 
          \onslide*<1-4|handout:1>{(\textcolor{functor}{\vindexpush}\sheafc_{(\gbasec, \gtotalc)})(\dbase)}
          \\
          \& \& \\
          \onslide*<1-4|handout:1>{(\textcolor{functor}{\vindexpull}\sheafc_{(\dbasec, \dtotalc)})(\gbasec)}
          \onslide*<1-3|handout:1>{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}
          \onslide*<4-|handout:2->{\arrow[rr, "\vindexpullc", color=artist]}
          \onslide*<2-3|handout:1>{\arrow[uu, "\textcolor{nattran}{Nat_{\gbasec}}", color=nattran]} 
          \onslide*<4-|handout:2->{\arrow[uu, "\vartistc_{\vindexpushc}", color=artist]}
          \&  \& 
          \onslide*<1-4|handout:1->{\sheafc_{\dbasec, \dtotalc}} 
          \onslide*<2-3|handout:1>{\arrow[uu, "\textcolor{nattran}{Nat_{\dbasec}}"', color=nattran]}
          \onslide*<4-|handout:2->{\arrow[uu, "\vartistc_{\vindexpullc}"', color=artist]}
          \onslide*<3|handout:1>{\arrow[lluu, " "' description, dashed, color=nattran]}
          \onslide*<4-|handout:2->{\arrow[lluu, "\vartistc"' description, dashed, color=artist]}
        \end{tikzcd}
      \end{equation*}

@@

@@

\begin{frame}{Continuty Equivariance $\vindexpullc\hat\dfuncc = \hat\dfuncc|_{\vindexprec}$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement =\&]
            S 
            \arrow[r, "\xi"] 
            \arrow[d, "\xi^*\hat\varphi"'] 
            \& 
            K 
            \arrow[d, "\hat\varphi"] \\
            S^{\prime} 
            \arrow[r, "\xi"]
            \& 
            K^{\prime}
            \end{tikzcd}
    \end{equation*}
\end{frame}
\begin{frame}{Field Equivariance $\tilde\dfuncc \cong \tilde\dfuncc_\gtotalc$}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        {\Gamma(U, E)} 
        \arrow[r, "A"] 
        \arrow[d, "\tilde\varphi\circ\hat\varphi_*"'] 
        \& 
        {\Gamma(W, H)} 
        \arrow[d, "\tilde\varphi_H\circ\xi_*\hat{\varphi}_*"] \\
        {\Gamma(\hat\varphi U, \tilde\varphi\hat\varphi_*E)} 
        \arrow[r, "A"] 
        \& 
        {\Gamma(\xi^*\hat\varphi W, \tilde\varphi_H\xi^*\hat\varphi_*H)}    
    \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{frame}{Equivariant Artist}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        {\mathcal{O}_{K, E}} 
        \arrow[r, "A"] 
        \arrow[d, "\varphi"'] \& 
        {\mathcal{O}_{S,H}} 
        \arrow[d, "\varphi_H"] \\
        {\mathcal{O}_{K^{\prime}, E^{\prime}}} 
        \arrow[r, "A"]    \& 
        {\mathcal{O}_{S^{\prime}, H^{\prime}}}    
        \end{tikzcd} 
    \end{equation*}
        \begin{block}
            \vartistc\ is equivariant if and only if there exists a $\dfuncc_H$ s.t the diagram commutes. 
            \begin{equation*}
            \end{equation*}
        \end{block}
    \end{frame}
